A Comparison of Graph Processing Systems

### 2020-09-12 documentation/paper/sections/preliminiaries.tex
more consistency and todos
clean up repository and one more todo
paper preliminiaries push and pull variants

\section{Preliminaries}
TODO //

@@

\subsection{Push and Pull Variants}
\todo{}

@@

>>>>

\section{Preliminaries}
\todo{Section beschreiben}

@@

\subsection{Push and Pull Variants}
Many parallel graph algorithms, as well as the three we consider here, are implemented by iterating over vertices, or edges \cite{Galois}.
The respective vertex or edge, which is considered in an iteration, is also called \emph{active} vertex or edge.
Applying an operator to this \emph{active} vertex or edge is called an \emph{activity}.
This operator considers always only a local so called \emph{neighborhood} to the \emph{active} vertex or edge.
To this \emph{neighborhood} belong only vertices and edges, which are in the direct surrounding of the \emph{active} vertex or edge, which allows to parallelise the iteration relatively easy.

In general such an operator can change the structure of the \emph{neighbourhood} too.
But in the following we assume, that an operator changes only \emph{labels} of vertices or edges in the \emph{neighbourhood}.
Often this operator can be implemented in two different ways, called \emph{push style} or \emph{pull style}.
A \emph{push-style} operator reads the value of the \emph{active} vertex or edge and updates the values of its \emph{neighborhood}.
In contrast the \emph{pull-style} operator reads all values of its \emph{neighborhood} and updates the value of the \emph{active} vertex or edge.

\emph{Pull-style} operators need less synchronization in parallel implementations, because unlike \emph{pull style} there is only one write and many read operations. Thus locks can be avoided. So \emph{push-style} operators are more efficient, if there are only a few \emph{active} vertices or edges at the same time, or the \emph{neighborhoods} do not overlap, which can not be avoided in general. On the other hand \emph{pull-style} operators are more efficient, if there are many \emph{active} vertices or edges at the same time.

@@

\subsection{NUMA-awareness}
\todo{Section}
